\begin{singlespace}
\begin{longtable}{p{0.3\linewidth}p{0.7\linewidth}}
\caption{Data science terms: Interpretation}\\
\hline
\makecell[r]{\textbf{Intelligibility}} & Similar to interpretability, can processes or results be understood by humans. However, not all humans understand equally. So perhaps
intelligibiilty is context-dependent.\\
\makecell[r]{\textbf{Evaluation}\\ \textbf{(of interpretation)}} & An interpretation is an intelligible assertion about the world that may be evaluated in various ways, such as usefulness,
or validation by quantifyable proxy.\\
\makecell[r]{\textbf{Explainability}} & Explaining model behavior, why or how a result is generated. Interpretability is necessary but not sufficient for explainability.\\
\makecell[r]{\textbf{Completeness}} & Accuracy of explanations. A simplified, less-complete explanation may be intelligible and pursuasive, but potentially misleading or
unethical.\\
\makecell[r]{\textbf{Contrastive explanation}} & Explaining a result by contrast with a different case. E.g. Why was my application rejected but this other one accepted?\\
\makecell[r]{\textbf{Algorithmic Transparency}} & Opposite of opacity and black-boxes, can the system's processes by investigated.\\
\makecell[r]{\textbf{Algorithmic Fairness}} & Are results unbiased? In some domains could violate legal anti-discrimination protections. In research science, could raise COI
concerns.\\
\makecell[r]{\textbf{Accountability}} & Related to transparency, can methods and results be accounted for algorithmically. E.g. waiter, how was this service charge calculated?
And how was the price of the paella determined from the ingredient list, labor costs, and overhead?\\
\makecell[r]{\textbf{Black-box system}} & Non-transparent, opaque system, not explainable since the specifics of the process for generating a result are inaccessible.\\
\makecell[r]{\textbf{Pursuasive systems}} & Human opinions and decisions can be affected, and systems can be optimized for pursuasiveness, but accuracy may be compromised.\\
\makecell[r]{\textbf{Context-aware systems}} & For HCI issues of Interaction Design and Learnability, context-aware systems connect the application logic to the user and UI
designer. \\
\makecell[r]{\textbf{iML}} & Interpretable ML\\
\makecell[r]{\textbf{FATML}} & Fair, accountable and transparent ML\\
\makecell[r]{\textbf{XAI}} & Explainable AI, a term favored by US-DARPA.\\
\hline
\end{longtable}
\end{singlespace}
